Evolution of Processes in Delivering Reliable Software within the European Scientific Arena

### 2019-02-13 paper-jgc.tex
Small statement to justify the elaborated analysis of INDIGO with respect to the others

{\sl INDIGO--DataCloud} is the most recent project included in this paper, it
leveraged the lessons learned from the previous experiences described in
Section~\ref{sec:ev}. The expertise gathered throughout these years was highly
profitable regarding evaluation and application of innovative software engineering
methodologies, management of new technologies to put those methodologies
into practice, compilation and analysis of an appropriate set of metrics to measure the
quality of the implemented solutions.
An additional level of complexity, comes from the fact that these large collaborative projects
have an extensive list of partners.

>>>>

{\sl INDIGO--DataCloud} is the most recent project included in this paper, it
leverages the lessons learned from the previous experiences described in
Section~\ref{sec:ev} and, consequently, it will be thoroughly analyzed. The expertise gathered throughout these years was highly
profitable regarding evaluation and application of innovative software engineering
methodologies, management of new technologies to put those methodologies
into practice, compilation and analysis of an appropriate set of metrics to measure the
quality of the implemented solutions.
An additional level of complexity, comes from the fact that these large collaborative projects
have an extensive list of partners.
